\normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range}

### 2017-07-08 Manuscript.Rmd
Added equation numbering

@@

windowsFonts(Times=windowsFont("TT Times New Roman"))

# source('./update_ref.R')
# update_ref()
```

```{r, load packages}

suppressPackageStartupMessages({
  library(RColorBrewer)
  library(colorRamps)
  library(stargazer)
  library(sandwich)
  library(lmtest)
  library(broom)
  library(tmap)
  library(tmaptools)
  library(rgdal)
  library(sp)
  library(RefManageR)
  library(tidyverse)
})

@@

$$TW = aTL^b$$

@@

$$log_{10}(TW) = blog_{10}TL + log{10}(a)$$

@@

$$Y = mX + c$$
Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$. This equation was used to estimate the coefficients ($a$ and $b$), which were estimated via an Ordinary Least Square Regression and heteroskedastic-robust; Standard Errors were calculated to account for **lo que sea que Olivier dijo que era importante**.

>>>>

<script type="text/x-mathjax-config">
MathJax.Hub.Config({
  TeX: { 
      equationNumbers: { 
            autoNumber: "all",
            formatNumber: function (n) {return '9.'+n}
      } 
  }
});
</script>

@@

windowsFonts(Times=windowsFont("TT Times New Roman"))
```

```{r load packages}
suppressPackageStartupMessages({
  library(RColorBrewer)
  library(colorRamps)
  library(stargazer)
  library(sandwich)
  library(lmtest)
  library(broom)
  library(tmap)
  library(tmaptools)
  library(rgdal)
  library(sp)
  library(RefManageR)
  library(tidyverse)
})

@@

\begin{equation}TW = aTL^b\end{equation}

@@

\begin{equation}log_{10}(TW) = blog_{10}TL + log{10}(a)\end{equation}

@@

\begin{equation}Y = mX + c\end{equation}

Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$. This equation was used to estimate the coefficients ($a$ and $b$), which were estimated via an Ordinary Least Square Regression and heteroskedastic-robust; Standard Errors were calculated to account for **lo que sea que Olivier dijo que era importante**.
